Localisation and Sensor Privacy Using the Extended Information Filter and Secure Weighted Aggregation

### 2020-07-14 main.tex
Added bib to link with zotero Updated and added more points for paper layout

Encryption schemes involve formal indistinguishability proofs typically over bit-streams or integers. They typically reply on computationally hard problems over bit streams of a sufficiently large size; therefore the additional computational requirements of using encryption schemes should be pointed out and what this means in a real-time distributed sensor system. Continuing, specify public key cryptography applicability to distributed systems; difference to symmetric schemes. Homomorphic encryption power and use case.

@@

% Maybe rename this to Our Scheme or something like that
\section{Private Weighted Aggregation}
\subsection{Proof}
Give the reduction proof here for pWSAO and implicit indistinguishability of weights

@@

\subsection{Localisation Measurement Modification}
Show here the weighted integrals that give mean and variance of the new noise.

@@

\section{Conclusion}

>>>>

Encryption schemes involve formal indistinguishability proofs typically over bit-streams or integers. They typically reply on computationally hard problems over bit streams of a sufficiently large size; therefore the additional computational requirements of using encryption schemes should be pointed out and what this means in a real-time distributed sensor system. Continuing, specify public key cryptography applicability to distributed systems; difference to symmetric schemes. Homomorphic encryption power and use case. Why FHE isn't used often, why additive partially homomorphic encryption is.

@@

% Maybe rename this to Our Scheme or something like that
\section{Private Weighted Aggregation}
\subsection{Proof}
Give the reduction proof here for pWSAO and implicit indistinguishability of weights. alternatively sketch it out here and give reduction in appendix.

@@

\subsection{Localisation Measurement Modification}
Show here the weighted integrals that give mean and variance of the new noise. If wanting to show more working, do this in appendix section, but probablynot needed.

@@

\section{Conclusion}
Future work can include hardware implementations, measurement handling which preservers Gaussian noise, or non-Gaussian noise methods. Can also consider ways of sending less information form the navigator to the sensors at each time step.
